Machine Learning for Predictive Auto-Tuning with Boosted Regression Trees

### 2012-03-07 paper/final.tex

Other directions will include the validation of our predictive
auto-tuning framework to other domains and environments, in particular
general data-parallel primitives and non data-parallel applications,
other multi-core heterogeneous architectures, and software platforms
such as OpenCL.

>>>>

Other directions will include the validation of our predictive
auto-tuning framework to other domains and environments, in particular
general data-parallel primitives and non data-parallel applications,
other multi-core architectures, and heterogeneous software platforms
such as OpenCL.
